Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-26 documents/mixtures/mixture_models.tex
move todo list to github
now with eps files; done for submission; about to revert

% to-do
% -----
% - HOGG: send to Bertin and Rix and Peng and Lupton and Bundy for comments
% - HOGG: submit!
% - HOGG: post on arXiv
% - HOGG: can we drop the regularization in the badness and still succeeed?  If so, let's do that (and drop it in the text).
% - HOGG: make what I say about M=6 lux and M=8 lux true -- ie, edit the Tractor code!
% - HOGG: should we make Machine Readable Tables for PASP?  Yes.

\documentclass[12pt,pdftex,preprint]{aastex}
\usepackage{amssymb,amsmath,mathrsfs}

@@

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.pdf}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_fractional_log.pdf}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown fractionally and logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.pdf}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.pdf}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile.pdf}%
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile_log.pdf}
\caption{The lux and luv profiles and approximations.  The panels are
  equivalent to those in the top-row of \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{ser2_K10_MR08_profile_log.pdf}%
\includegraphics[width=\figurewidth]{ser3_K10_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{ser5_K10_MR08_profile_log.pdf}%
\includegraphics[width=\figurewidth]{mixtures_vs_model_K10.pdf}
\caption{Three ser profiles---with $n=2$, $3$, and $5$---and
  approximations.  The top-left, top-right, and bottom-left panels are
  equivalent to those in the top-right of \figurename~\ref{fig:exp}.
  \textsl{bottom-right:} The dependence on the amplitudes $a^{\ser(n)}_m$
  and root-variances $\sqrt{v^{\ser(n)}_m}$ on ser index $n$.\label{fig:ser}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.\label{fig:M}}
\end{figure}

\clearpage
\begin{figure}
\setlength{\figurewidth}{0.25\textwidth}
\begin{tabular}{@{}c@{}c@{}}
\includegraphics[width=\figurewidth]{trdemo-01} &
\includegraphics[width=\figurewidth]{trdemo-02} \\
\includegraphics[width=\figurewidth]{trdemo-03} &
\includegraphics[width=\figurewidth]{trdemo-06} \\
\includegraphics[width=\figurewidth]{trdemo-08} &
\includegraphics[width=\figurewidth]{trdemo-09}
\end{tabular}
\caption{Demonstration of use of the profiles, or the implicit
  generative model in this \documentname.  \textsl{top-left:} The
  circular dimensionless $M^{\luv}=8$ mixture-of-Gaussian
  approximation to the luv profile, represented on a very fine pixel
  grid. \textsl{top-right:} The ellipse representing the non-trivial
  affine transformation to be applied to the circular, dimensionless
  profile.  \textsl{middle-left:} The sheared profile.
  \textsl{middle-right:} A $K=3$ mixture-of-Gaussian model of the
  pixel-convolved point-spread function, represented on the very fine
  pixel grid.  \textsl{bottom-left:} The sheared profile convolved
  with the PSF, represented on the very fine pixel grid.
  \textsl{bottom-right:} The sheared luv convolved with the PSF, but
  now shown on a realistic pixel grid.  Because by assumption the PSF
  is a pixel-convolved PSF, the representation on the realistic grid
  is found simply by interpolating to the pixel centers the
  mixture-component Gaussians.\label{fig:example}}
\end{figure}

>>>>

\documentclass[12pt,preprint]{aastex}
\usepackage{amssymb,amsmath,mathrsfs}

@@

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.eps}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.eps}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.eps}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_fractional_log.eps}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown fractionally and logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.eps}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.eps}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.eps}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.eps}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile.eps}%
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile_log.eps}\\
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile.eps}%
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile_log.eps}
\caption{The lux and luv profiles and approximations.  The panels are
  equivalent to those in the top-row of \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{ser2_K10_MR08_profile_log.eps}%
\includegraphics[width=\figurewidth]{ser3_K10_MR08_profile_log.eps}\\
\includegraphics[width=\figurewidth]{ser5_K10_MR08_profile_log.eps}%
\includegraphics[width=\figurewidth]{mixtures_vs_model_K10.eps}
\caption{Three ser profiles---with $n=2$, $3$, and $5$---and
  approximations.  The top-left, top-right, and bottom-left panels are
  equivalent to those in the top-right of \figurename~\ref{fig:exp}.
  \textsl{bottom-right:} The dependence on the amplitudes $a^{\ser(n)}_m$
  and root-variances $\sqrt{v^{\ser(n)}_m}$ on ser index $n$.\label{fig:ser}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp.eps}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev.eps}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux.eps}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv.eps}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.\label{fig:M}}
\end{figure}

\clearpage
\begin{figure}
\setlength{\figurewidth}{0.25\textwidth}
\begin{tabular}{@{}c@{}c@{}}
\includegraphics[width=\figurewidth]{trdemo-01.eps} &
\includegraphics[width=\figurewidth]{trdemo-02.eps} \\
\includegraphics[width=\figurewidth]{trdemo-03.eps} &
\includegraphics[width=\figurewidth]{trdemo-06.eps} \\
\includegraphics[width=\figurewidth]{trdemo-08.eps} &
\includegraphics[width=\figurewidth]{trdemo-09.eps}
\end{tabular}
\caption{Demonstration of use of the profiles, or the implicit
  generative model in this \documentname.  \textsl{top-left:} The
  circular dimensionless $M^{\luv}=8$ mixture-of-Gaussian
  approximation to the luv profile, represented on a very fine pixel
  grid. \textsl{top-right:} The ellipse representing the non-trivial
  affine transformation to be applied to the circular, dimensionless
  profile.  \textsl{middle-left:} The sheared profile.
  \textsl{middle-right:} A $K=3$ mixture-of-Gaussian model of the
  pixel-convolved point-spread function, represented on the very fine
  pixel grid.  \textsl{bottom-left:} The sheared profile convolved
  with the PSF, represented on the very fine pixel grid.
  \textsl{bottom-right:} The sheared luv convolved with the PSF, but
  now shown on a realistic pixel grid.  Because by assumption the PSF
  is a pixel-convolved PSF, the representation on the realistic grid
  is found simply by interpolating to the pixel centers the
  mixture-component Gaussians.\label{fig:example}}
\end{figure}
